---
title: "plotr"
output: 
  flexdashboard::flex_dashboard:
    navbar:
     - { title: "Developed by PainblogR", icon: 'fa-home', href: "https://www.painblogr.org", align: right }
    social: ['menu']
    source_code: 'https://github.com/kamermanpr/painblogr-plotr.git'
runtime: shiny
---

```{r setup, include = FALSE}
library(flexdashboard)
library(shiny)
library(readr)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggforce)
```

```{r eval = FALSE}
# Packages
library(stringr)
library(palmerpenguins)

# Datasets
## Long format
### Iris
iris %>% 
    write_csv(file = 'data/iris_original.csv')

iris %>% 
    group_by(Species) %>% 
    slice_head(n = 8) %>% 
    ungroup() %>% 
    slice_sample(n = 24) %>% 
    mutate(ID = str_pad(as.character(row_number()), 
                        width = 3, 
                        side = 'left',
                        pad = '0')) %>% 
    select(ID, Species, everything()) %>% 
    write_csv(file = 'data/iris_n24.csv')

### Penguins
penguins %>% 
    write_csv(file = 'data/penguins_orginal.csv')

penguins %>% 
    group_by(species, island) %>% 
    slice_head(n = 5) %>% 
    ungroup() %>% 
    slice_sample(n = 25) %>% 
    mutate(ID = str_pad(as.character(row_number()), 
                        width = 3, 
                        side = 'left',
                        pad = '0')) %>% 
    select(ID, species, everything()) %>% 
    select(-year) %>% 
    write_csv(file = 'data/penguins_n25.csv')
```

Welcome {data-navmenu='Select a plot type'}
===================================== 

Welcome to the `plotr` app. 

To analyse your data, please try the companion app, [`statr`](https://kamermanpr.shinyapps.io/painblogr-statr/){ target='_blank' },

The app provides basic plot options, such as box-and-whisker plots, scatter plots, column graphs, and histograms. 

The app was developed by Peter Kamerman (GitHub: [kamermanpr](https://github.com/kamermanpr.git){ target='_blank' }) and Kavalin Nair (GitHub: [TripleBlackCat](https://github.com/TripleBlackCat.git){ target='_blank' }).

**To start, choose the type of plot you want from the drop-down menu labelled _“Select a plot type”_.**
    
Boxplot {data-navmenu='Select a plot type'}
=====================================  

Column {.sidebar data-width=350}
-------------------------------------

```{r boxplot_1}
h1('Boxplot')

p('If there is a grouping variable, import data in long format (see example:', a('here', href = 'https://drive.google.com/open?id=1--iOezcoFaE9C-x4JiT6zygNOKyrWNh0&authuser=peter.kamerman%40gmail.com&usp=drive_fs', target='_blank'), ').')

p('For download options, scroll to the bottom of this sidebar.')

hr()

# Upload file
fileInput(inputId = 'box_file0', 
          label = 'Import data',
          multiple = FALSE,
          accept = c('.csv'))

# Make reactive data
box_df <- reactive({
    req(input$box_file0)
    read_csv(input$box_file0$datapath, 
             show_col_types = FALSE)
})

# Select variables
## Response variable
output$box_yvar <- renderUI({
    varSelectInput(inputId = 'box_y_var',
                   label = 'Choose repsonse variable',
                   data = box_df())
    })

uiOutput('box_yvar')

## Grouping variable
output$box_groupvar <- renderUI({
    varSelectInput(inputId = 'box_group_var',
                   label = 'Choose grouping variable',
                   selected = NULL,
                   data = box_df())
    })

uiOutput('box_groupvar')

## Choose plot type
radioButtons(inputId = 'box_plot_type',
             label = 'Plot type',
             choices = c('Simple boxplot (default)' = 'box',
                         'Add beeswarm' = 'box_points',
                         'Add sina plot' = 'box_sina'),
             selected = 'box')

## Add labels
textInput(inputId = 'box_title', 
          label = 'Plot title',
          value = NULL)

textInput(inputId = 'box_y_label', 
          label = 'Y-axis label',
          value = NULL)

textInput(inputId = 'box_x_label', 
          label = 'X-axis label',
          value = NULL)

## Base font size
sliderInput(inputId = 'box_base_size',
            label = 'Font size',
            value = 18,
            min = 8,
            max = 28)

## Point size size
sliderInput(inputId = 'box_size',
            label = 'Point size (beeswarm and sina)',
            value = 3,
            min = 0,
            max = 10)

## Point transparency size
sliderInput(inputId = 'box_alpha',
            label = 'Point transparency (beeswarm and sina)',
            value = 1,
            min = 0,
            max = 1)

## Point scatter width
sliderInput(inputId = 'box_scatter_width',
            label = 'Scatter width (beeswarm and sina)',
            value = 0.3,
            min = 0,
            max = 1)

## Y-axis limits
numericInput(inputId = 'box_min_y',
             label = 'Minimum y-axis value',
             value = NULL)

numericInput(inputId = 'box_max_y',
             label = 'Maximum y-axis value',
             value = NULL)

hr()

h1('Download plot')

# Format
selectInput(inputId = 'box_format',
            label = 'Choose file format',
            selected = 'png',
            choices = c('bmp', 'jpg', 'pdf', 'png'))

# Plot width
numericInput(inputId = 'box_width',
             label = 'Figure width (cm)',
             value = 18)

## Plot height
numericInput(inputId = 'box_height',
             label = 'Figure height (cm)',
             value = 13)

# Add download button
output$box_download_button <- renderUI({
    downloadButton(outputId = 'boxplot_download_button',
                   label = "'Click' to download image")
    })

uiOutput('box_download_button')
```

Column
-------------------------------------

### Plot

```{r boxplot_2}
# Plot graph
output$box_plot <- renderPlot(
    if(req(input$box_plot_type) == 'box_points') {
        ggplot(data = box_df()) +
        aes(x = box_df()[[input$box_group_var]],
            y = box_df()[[input$box_y_var]]) +
        geom_boxplot() +
        geom_point(position = position_jitter(height = 0,
                                              width = input$box_scatter_width,
                                              seed = 1234),
                   shape = 21,
                   fill = '#000000',
                   alpha = input$box_alpha,
                   size = input$box_size) +
        geom_point(position = position_jitter(height = 0,
                                              width = input$box_scatter_width,
                                              seed = 1234),
                   shape = 21,
                   fill = NA,
                   colour = '#000000',
                   size = input$box_size) +
        labs(title = input$box_title,
             y = input$box_y_label,
             x = input$box_x_label) +
        scale_y_continuous(limits = c(input$box_min_y, input$box_max_y)) +
        theme_minimal(base_size = input$box_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$box_base_size),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else if(req(input$box_plot_type) == 'box_sina'){
        
        ggplot(data = box_df()) +
        aes(x = box_df()[[input$box_group_var]],
            y = box_df()[[input$box_y_var]]) +
        geom_boxplot(position = position_nudge(x = -0.2),
                     width = 0.3) +
        geom_sina(position = position_nudge(x = 0.2),
                  maxwidth = input$box_scatter_width,
                  seed = 1234,
                  shape = 21,
                  fill = '#000000',
                  alpha = input$box_alpha,
                  size = input$box_size) +
        geom_sina(position = position_nudge(x = 0.2),
                  maxwidth = input$box_scatter_width,
                  seed = 1234,
                  shape = 21,
                  fill = NA,
                  colour = '#000000',
                  size = input$box_size) + 
        labs(title = input$box_title,
             y = input$box_y_label,
             x = input$box_x_label) +
        scale_y_continuous(limits = c(input$box_min_y, input$box_max_y)) +
        theme_minimal(base_size = input$box_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$box_base_size),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else {
        
        ggplot(data = box_df()) +
        aes(x = box_df()[[input$box_group_var]],
            y = box_df()[[input$box_y_var]]) +
        geom_boxplot() +
        labs(title = input$box_title,
             y = input$box_y_label,
             x = input$box_x_label) +
        scale_y_continuous(limits = c(input$box_min_y, input$box_max_y)) +
        theme_minimal(base_size = input$box_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$box_base_size),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    }
)

plotOutput('box_plot')
```

```{r boxplot_3}
# Download plot
output$boxplot_download_button <- downloadHandler(
    filename = function() {
        paste0('boxplot_', Sys.Date(), '.', input$box_format)
    },
    content = function(file) {
        plotOutput('box_plot')
        ggsave(file, 
               width = input$box_width, 
               height = input$box_height,
               units = 'cm')
    }
  )
```

Scatter plot {data-navmenu='Select a plot type'}
=====================================  

Column {.sidebar data-width=350}
-------------------------------------

```{r scatter_1}
h1('Scatter plot')

p('If there is a grouping variable, import data in long format (see example:', a('here', href = 'https://drive.google.com/open?id=1--iOezcoFaE9C-x4JiT6zygNOKyrWNh0&authuser=peter.kamerman%40gmail.com&usp=drive_fs', target='_blank'), ').')

p('For download options, scroll to the bottom of this sidebar.')

hr()

# Upload file
fileInput(inputId = 'scatter_file0', 
          label = 'Import data',
          multiple = FALSE,
          accept = c('.csv'))

# Make reactive data
scatter_df <- reactive({
    req(input$scatter_file0)
    read_csv(input$scatter_file0$datapath, 
             show_col_types = FALSE)
})

# Select variables
## Y variable
output$scatter_yvar <- renderUI({
    varSelectInput(inputId = 'scatter_y_var',
                   label = 'Choose repsonse variable',
                   data = scatter_df())
    })

uiOutput('scatter_yvar')

## X variable
output$scatter_xvar <- renderUI({
    varSelectInput(inputId = 'scatter_x_var',
                   label = 'Choose repsonse variable',
                   data = scatter_df())
    })

uiOutput('scatter_xvar')

output$scatter_groupvar <- renderUI({
    selectInput(inputId = 'scatter_group_var',
            label = 'Choose grouping variable (optional)',
            selected = NULL,
            choices = c('None', names(scatter_df())))
})

uiOutput('scatter_groupvar')

## Add regression or loess curve
radioButtons(inputId = 'scatter_smooth',
             label = 'Add regression line',
             choices = c('None (default)' = 'none',
                         'Linear regression' = 'linear',
                         'LOESS curve' = 'loess'),
             selected = 'none')

## Add labels
textInput(inputId = 'scatter_title', 
          label = 'Plot title',
          value = '')

textInput(inputId = 'scatter_y_label', 
          label = 'Y-axis label',
          value = '')

textInput(inputId = 'scatter_x_label', 
          label = 'X-axis label',
          value = '')

## Base font size
sliderInput(inputId = 'scatter_base_size',
            label = 'Font size',
            value = 18,
            min = 8,
            max = 28)

## Point size size
sliderInput(inputId = 'scatter_size',
            label = 'Point size',
            value = 3,
            min = 0,
            max = 10)

## Point transparency size
sliderInput(inputId = 'scatter_alpha',
            label = 'Point transparency',
            value = 1,
            min = 0,
            max = 1)

## Colour scheme
selectInput(inputId = 'scatter_colours',
            label = 'Colour scheme (used with grouping variable)',
            selected = NULL,
            choices = c('Default (20 colours)' = 'Tableau 20',
                        'Tableau (10 colours)' = 'Tableau 10',
                        'Colour blind (10 colours)' = 'Color Blind',
                        'Grey (5 colours)' = 'Classic Gray 5'))

## Legend position
### x value
sliderInput(inputId = 'scatter_x_legend',
            label = 'Legend position (x-axis coordinate)',
            value = 0.85,
            min = 0,
            max = 1)

### y-value
sliderInput(inputId = 'scatter_y_legend',
            label = 'Legend position (y-axis coordinate)',
            value = 0.85,
            min = 0,
            max = 1)

## Y-axis limits
numericInput(inputId = 'scatter_min_y',
             label = 'Minimum y-axis value',
             value = NULL)

numericInput(inputId = 'scatter_max_y',
             label = 'Maximum y-axis value',
             value = NULL)

## X-axis limits
numericInput(inputId = 'scatter_min_x',
             label = 'Minimum x-axis value',
             value = NULL)

numericInput(inputId = 'scatter_max_x',
             label = 'Maximum x-axis value',
             value = NULL)

hr()

h1('Download plot')

# Format
selectInput(inputId = 'scatter_format',
            label = 'Choose file format',
            selected = 'png',
            choices = c('bmp', 'jpg', 'pdf', 'png'))

# Plot width
numericInput(inputId = 'scatter_width',
             label = 'Figure width (cm)',
             value = 16)

## Plot height
numericInput(inputId = 'scatter_height',
             label = 'Figure height (cm)',
             value = 16)

# Add download button
output$scatter_download_button <- renderUI({
    downloadButton(outputId = 'scatterplot_download_button',
                   label = "'Click' to download image")
    })

uiOutput('scatter_download_button')
```

Column
-------------------------------------

### Plot

```{r scatter_2}
# Plot graph
output$scatter_plot <- renderPlot(
    
    if(req(input$scatter_smooth) == 'none' & req(input$scatter_group_var) == 'None'){
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]]) +
        geom_point(shape = 21,
                   colour = '#000000',
                   fill = '#000000',
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   colour = '#000000',
                   size = input$scatter_size) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else if(input$scatter_smooth == 'linear' & input$scatter_group_var == 'None'){
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]]) +
        geom_point(shape = 21,
                   colour = '#000000',
                   fill = '#000000',
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   colour = '#000000',
                   size = input$scatter_size) +
        geom_smooth(method = 'lm',
                    colour = '#000000',
                    size = 1,
                    se = FALSE) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else if(input$scatter_smooth == 'loess' & input$scatter_group_var == 'None'){
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]]) +
        geom_point(shape = 21,
                   colour = '#000000',
                   fill = '#000000',
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   colour = '#000000',
                   size = input$scatter_size) +
        geom_smooth(method = 'loess',
                    colour = '#000000',
                    size = 1,
                    se = FALSE) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else if(input$scatter_smooth == 'linear' & input$scatter_group_var != 'None'){
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]],
            fill = scatter_df()[[input$scatter_group_var]],
            colour = scatter_df()[[input$scatter_group_var]]) +
        geom_point(shape = 21,
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   fill = NA,
                   size = input$scatter_size) +
        geom_smooth(method = 'lm',
                    size = 1,
                    se = FALSE) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        scale_colour_tableau(palette = input$scatter_colours) +
        scale_fill_tableau(palette = input$scatter_colours) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else if(input$scatter_smooth == 'loess' & input$scatter_group_var != 'None'){
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]],
            fill = scatter_df()[[input$scatter_group_var]],
            colour = scatter_df()[[input$scatter_group_var]]) +
        geom_point(shape = 21,
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   fill = NA,
                   size = input$scatter_size) +
        geom_smooth(method = 'loess',
                    size = 1,
                    se = FALSE) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        scale_colour_tableau(palette = input$scatter_colours) +
        scale_fill_tableau(palette = input$scatter_colours) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    } else {
        
        ggplot(data = scatter_df()) +
        aes(x = scatter_df()[[input$scatter_x_var]],
            y = scatter_df()[[input$scatter_y_var]],
            fill = scatter_df()[[input$scatter_group_var]],
            colour = scatter_df()[[input$scatter_group_var]]) +
        geom_point(shape = 21,
                   alpha = input$scatter_alpha,
                   size = input$scatter_size) +
        geom_point(shape = 21,
                   fill = NA,
                   size = input$scatter_size) +
        geom_smooth(method = 'loess',
                    size = 1,
                    se = FALSE) +
        labs(title = input$scatter_title,
             y = input$scatter_y_label,
             x = input$scatter_x_label) +
        scale_x_continuous(limits = c(input$scatter_min_x, input$scatter_max_x)) +
        scale_y_continuous(limits = c(input$scatter_min_y, input$scatter_max_y)) +
        scale_colour_tableau(palette = input$scatter_colours) +
        scale_fill_tableau(palette = input$scatter_colours) +
        theme_minimal(base_size = input$scatter_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$scatter_base_size),
                  legend.position = c(input$scatter_x_legend, input$scatter_y_legend),
                  legend.title = element_blank(),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
    }
)

plotOutput('scatter_plot')
```

```{r scatter_3}
# Download plot
output$scatterplot_download_button <- downloadHandler(
    filename = function() {
        paste0('scatterplot_', Sys.Date(), '.', input$scatter_format)
    },
    content = function(file) {
        plotOutput('scatter_plot')
        ggsave(file, 
               width = input$scatter_width, 
               height = input$scatter_height,
               units = 'cm')
    }
  )
```

Histogram {data-navmenu='Select a plot type'}
=====================================  

Column {.sidebar data-width=350}
-------------------------------------

```{r histogram_1}
h1('Histogram')

p('The input must be a single continuous variable')

p('For download options, scroll to the bottom of this sidebar.')

hr()

# Upload file
fileInput(inputId = 'histo_file0', 
          label = 'Import data',
          multiple = FALSE,
          accept = c('.csv'))

# Make reactive data
histo_df <- reactive({
    req(input$histo_file0)
    read_csv(input$histo_file0$datapath, 
             show_col_types = FALSE)
})

# Select variables
## Response variable
output$histo_var <- renderUI({
    varSelectInput(inputId = 'histo_var',
                   label = 'Choose variable to be plotted',
                   data = histo_df())
    })

uiOutput('histo_var')

## Add labels
textInput(inputId = 'histo_title', 
          label = 'Plot title',
          value = NULL)

textInput(inputId = 'histo_y_label', 
          label = 'Y-axis label',
          value = 'Count')

textInput(inputId = 'histo_x_label', 
          label = 'X-axis label',
          value = NULL)

## Base font size
sliderInput(inputId = 'histo_base_size',
            label = 'Font size',
            value = 18,
            min = 8,
            max = 28)

## Bin width
numericInput(inputId = 'histo_bin_width',
             label = 'Bin width (in the units of measurement)',
             value = 1,
             min = 1)

## Bar transparency size
sliderInput(inputId = 'histo_alpha',
            label = 'Bar transparency',
            value = 0.6,
            min = 0,
            max = 1)

hr()

h1('Download plot')

# Format
selectInput(inputId = 'histo_format',
            label = 'Choose file format',
            selected = 'png',
            choices = c('bmp', 'jpg', 'pdf', 'png'))

# Plot width
numericInput(inputId = 'histo_width',
             label = 'Figure width (cm)',
             value = 18)

## Plot height
numericInput(inputId = 'histo_height',
             label = 'Figure height (cm)',
             value = 13)

# Add download button
output$histo_download_button <- renderUI({
    downloadButton(outputId = 'histogram_download_button',
                   label = "'Click' to download image")
    })

uiOutput('histo_download_button')
```

Column
-------------------------------------

### Plot

```{r histogram_2}
# Plot graph
output$histo_plot <- renderPlot(
    
        ggplot(data = histo_df()) +
        aes(histo_df()[[input$histo_var]]) +
        geom_histogram(binwidth = input$histo_bin_width,
                       fill = '#000000',
                       colour = '#000000',
                       alpha = input$histo_alpha) +
        labs(title = input$histo_title,
             y = input$histo_y_label,
             x = input$histo_x_label) +
        theme_minimal(base_size = input$histo_base_size) +
            theme(plot.background = element_rect(colour = '#FFFFFF',
                                                 fill = '#FFFFFF'),
                  plot.title = element_text(size = input$histo_base_size),
                  axis.text = element_text(colour = '#000000'),
                  axis.line = element_line(colour = '#000000',
                                           size = 0.5),
                  axis.ticks = element_line(colour = '#000000',
                                            size = 0.5),
                  panel.grid = element_blank())
        
        )

plotOutput('histo_plot')
```

```{r histogram_3}
# Download plot
output$histogram_download_button <- downloadHandler(
    filename = function() {
        paste0('histogram_', Sys.Date(), '.', input$histo_format)
    },
    content = function(file) {
        plotOutput('histo_plot')
        ggsave(file, 
               width = input$histo_width, 
               height = input$histo_height,
               units = 'cm')
    }
  )
```
